---
title: "Building POLI 2000"
author: Yue Hu
output: html_notebook
editor_options: 
  chunk_output_type: inline
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(pacman)
p_load(dotwhisker, ggplot2, interplot,# Visualization
       lubridate,# Applied
       # dependency
       readxl, haven, descr, stringi, stringr, arm, car, stargazer,
       broom, tibble, tidyr, purrr, dplyr) # data wrangling

set.seed(313)
```


This notebook records schedules and relevant information of building POLI 2000. 

# Important Dates 

* Opening Date: 2017-08-21
* Final Exam Report: 2017-11-28
* Final Week: 2017-12-11
* Final Grade Approved: 2017-12-20

```{r}
# Opening Date: 2017-08-21 ####
start <- ymd("2017-08-21")
# Final Week: 2017-12-11 ####
end <- ymd("2017-12-17")
```

# Class Weeks
```{r}
over <- interval(start, end)
numWeek <- week(end) - week(start)
```

This semester includes `r numWeek` weeks. 
Ignoring the thanksgiving week and final week, there are `r numWeek - 2` instructing weeks.

```{r}
dates <- data.frame(day = seq(from = start, to = end, by = "days")) %>%
  mutate(day = ymd(day), weekDay = wday(day), weekNum = week(day),
         weekNum = weekNum - (min(weekNum) - 1)) %>% # get the relative week number
    filter(weekDay %in% c(2,1)) %>% # only keep Monday and Friday
      spread(key = weekDay, value = day) %>% # long to wide
        rename(Sun = `1`, Mon = `2`) %>%
          mutate(Sun = lead(Sun)) # get the Sundays to the correct rows
      
dates <- dates[c("weekNum", "Mon", "Sun")] %>% # reorder colums
  na.omit
dates
```

# Holidays 
* 2017-09-04: University Holiday
* 2017-11-19/2017-11-26: Thanksgiving
```{r}
dates$holiday <- NA
dates$holiday[dates$Mon == ymd("2017-09-04")] <- "Labor Day"
dates$holiday[dates$Mon == ymd("2017-11-20")] <- "Thanks Giving Week"
dates$holiday[dates$Mon == ymd("2017-12-11")] <- "Final Week"


dates
```

# Text book 
* Babbie, Earl. 2010. The Practice of Social Research (12th Edition). Belmont, CA:
Wadsworth-Cengage Learning.
* Kenneth Hoover; Todd Donovan. 1995. The Elements of Social Science Thinking, St. Martin's Press
* Shively, W. Phillips (2013). The Craft of Political Research. Boston: Pearson.

# Prelimiary schedule
```{r}
dates$content[is.na(dates$holiday)] <- c("Intro", "Scientific Research", "Concept", "Theory", "Measurement", "Validity", "Design: Experiment", "Case Description", "Case Comparison", "Case Selection", "Large-N", "Profession", "Ethnicity", "Presentation")

dates
```

