---
title: "Reading Guideline"
author: "Yue Hu"
output: html_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(pacman)
p_load(dotwhisker, ggplot2, interplot,# Visualization
       lubridate, RefManageR,# Applied
       # dependency
       readxl, haven, descr, stringi, stringr, arm, car, stargazer,
       broom, tidyverse) # data wrangling

set.seed(313)
```

```{r calendar, include=FALSE}
# Opening Date: 2017-08-21 ####
start <- ymd("2017-08-21")
# Final Week: 2017-12-11 ####
end <- ymd("2017-12-17")

dates <- data.frame(day = seq(from = start, to = end, by = "days")) %>%
  mutate(day = ymd(day), weekDay = wday(day), weekNum = week(day)) %>% # get the relative week number
  mutate(weekNum = weekNum - (min(weekNum) - 1)) %>%
    filter(weekDay %in% c(2,4)) %>% # only keep Monday and Wednesday
      spread(key = weekDay, value = day) %>% # long to wide
        rename(Mon = `2`, Wed = `4`)

dates$content <- NA
## Holidays
dates$content[dates$Mon == ymd("2017-09-04")] <- "What's A Good Question (Labor Day)"
dates$content[dates$Mon == ymd("2017-11-20")] <- "Thanks Giving Break"
dates$content[dates$Mon == ymd("2017-12-11")] <- "Final Week"

dates$content[is.na(dates$content)] <- c("Being a Political Scientist", "I'm A Scientist", "Where Does the Questions Come From", "What's A Concept", "Let's Measure Politics", "Measurement in Practice", "What's A Theory?", "Theory and Causal Inference", "Experimenting on Politics", "Principles of Case Study", "Case Study in Practice", "A Glance of Other Small-N Methods", "Understanding Large-N Analyses", "Professionalization")

weekList <- paste0("Week ", dates$weekNum, " (", dates$Mon, "/", dates$Wed, "): ", dates$content)
```

## `r weekList[1]`
This is the first week of our class.
As the beginning, you will read articles from two big names in political science.
In the articles they discuss what's political science and how to be a qualified political scientist. 
You are recommend to read Koehane (2009) first and then King (2006) and try to answer the following questions.

* According to Koehane, what's political science, and with what's the crucial character a political scientist need to equip themselves? 
* What's an inference? What's the different between the so-called "descriptive" and "causal" inferences?
* Why should we care about reliability and validity in inferences?
* Why is experiment the best way to explore causal inferences?
* Why do the standards in natural science not fit political science well in Koehane's view?
* What's the way King suggest to start a research project? What's the benefit? Are there other ways?
* Why does King emphasize to have a minimal-change version before a fully-improved version in the replications?


## `r weekList[2]`


## `r weekList[3]`

## `r weekList[4]`

## `r weekList[5]`

## `r weekList[6]`

## `r weekList[7]`
*Due for the research question approval: `r dates$Wed[7]`.*


## `r weekList[8]`


## `r weekList[9]`

## `r weekList[10]`


## `r weekList[11]`

## `r weekList[12]`


## `r weekList[13]`

*Due for the brief of the theory: `r dates$Mon[13]`.*

## `r weekList[14]`

## `r weekList[15]`


## `r weekList[16]`

## `r weekList[17]`
*Due for the research proposal: `r dates$Mon[17]`.*
