---
title: "Reading Guideline"
author: "Yue Hu"
output: html_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(pacman)
p_load(dotwhisker, ggplot2, interplot,# Visualization
       lubridate, RefManageR,# Applied
       # dependency
       readxl, haven, descr, stringi, stringr, arm, car, stargazer,
       broom, tidyverse) # data wrangling

set.seed(313)
```

```{r calendar, include=FALSE}
# Opening Date: 2017-08-21 ####
start <- ymd("2017-08-21")
# Final Week: 2017-12-11 ####
end <- ymd("2017-12-17")

dates <- data.frame(day = seq(from = start, to = end, by = "days")) %>%
  mutate(day = ymd(day), weekDay = wday(day), weekNum = week(day)) %>% # get the relative week number
  mutate(weekNum = weekNum - (min(weekNum) - 1)) %>%
    filter(weekDay %in% c(2,4)) %>% # only keep Monday and Wednesday
      spread(key = weekDay, value = day) %>% # long to wide
        rename(Mon = `2`, Wed = `4`)

dates$content <- NA
## Holidays
dates$content[dates$Mon == ymd("2017-09-04")] <- "What's A Good Question (Labor Day)"
dates$content[dates$Mon == ymd("2017-11-20")] <- "Thanks Giving Break"
dates$content[dates$Mon == ymd("2017-12-11")] <- "Final Week"

dates$content[is.na(dates$content)] <- c("Being a Political Scientist", "Being A Scientist First!", "Where Does A Question Come From?", "What's A Concept?", "Let's Measure Politics!", "Measurement in Practice", "What's A Theory?", "Theory and Causal Inference", "Experimenting on Politics", "Principles of Case Study", "Case Study in Practice", "A Glance of Other Small-N Methods", "Understanding Large-N Analyses", "Professionalization")

weekList <- paste0("Week ", dates$weekNum, " (", dates$Mon, "/", dates$Wed, "): ", dates$content)
```

## `r weekList[1]`
This is the first week of our class.
As the beginning, you will read articles by two big names in political science.
They discuss what's political science and how to be a qualified political scientist. 
You are recommend to read Koehane (2009) first and then King (2006).
Try to find the answers to the following questions during your reading.

* According to Koehane, what's political science, and what's the crucial character of political scientists (and students in political science)? 
* What does inference mean in political science research? How are the so-called "descriptive" and "causal" inferences different from each other?
* Why should we care about reliability and validity of inferences?
* Why is experiment the best way to detect causal inferences?
* Do the standards in natural science fit political science? Why or why not?
* What's the way King suggests to start a research project? Why does he recommend it?
* Why does King emphasize to offer a minimal-change analysis before a fully-improved analysis in the replications?


## `r weekList[2]`
From this week, we formally start our journey towards being a political scientist.
The first step is to understand how political scientists (or social scientists in general) contribute to improve the insight into human society. 
The first part of Babbie discusses how social scientific inquiries are different from ordinary human inquiries and why they are important and valuable.
The second part of Babbie together with King's influential piece discusses the regular procedure (*please recall how important following a certain procedure is for political science research from last week.*) to conduct a valid and solid social science research.

Try to think about the following questions when you read the readings:
* Babbie starts with discussing two fundamental ways to accumulate knowledge. How does it relate to the so-called "two pillars of science"?
* What are the relationship among the three ordinary sources of knowledge (human inquiry, tradition, and authority)? How would they mislead us from finding the reality?
* How is scientific theory different from philosophy?
* What are the three main purposes of social research?
* Babbie discusses three dialects in social research, which one is the most important?
* In Babbie's discussion about how to design a research project, what's the relationship between theoretical and empirical blocks?
* According to King, what's the purpose to do replication and why it is important for political science?
* How many steps are in a qualified replication? Are all of them necessary?
* Is there any case that we should withhold the data?
* Why are we worrying ourselves with what might be called "duplication" of misting research? Isn't the more important question actual replication where the same measurements are applied to new substantive areas, countries, or time periods?

<!-- ## `r weekList[3]` -->

<!-- ## `r weekList[4]` -->

<!-- ## `r weekList[5]` -->

<!-- ## `r weekList[6]` -->

<!-- ## `r weekList[7]` -->
<!-- *Due for the research question approval: `r dates$Wed[7]`.* -->


<!-- ## `r weekList[8]` -->


<!-- ## `r weekList[9]` -->

<!-- ## `r weekList[10]` -->


<!-- ## `r weekList[11]` -->

<!-- ## `r weekList[12]` -->


<!-- ## `r weekList[13]` -->

<!-- *Due for the brief of the theory: `r dates$Mon[13]`.* -->

<!-- ## `r weekList[14]` -->

<!-- ## `r weekList[15]` -->


<!-- ## `r weekList[16]` -->

<!-- ## `r weekList[17]` -->
<!-- *Due for the research proposal: `r dates$Mon[17]`.* -->
