---
title: "Reading Guideline"
author: "Yue Hu"
output: html_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(pacman)
p_load(dotwhisker, ggplot2, interplot,# Visualization
       lubridate, RefManageR,# Applied
       # dependency
       readxl, haven, descr, stringi, stringr, arm, car, stargazer,
       broom, tidyverse) # data wrangling

set.seed(313)
```

```{r calendar, include=FALSE}
# Opening Date: 2017-08-21 ####
start <- ymd("2017-08-21")
# Final Week: 2017-12-11 ####
end <- ymd("2017-12-17")

dates <- data.frame(day = seq(from = start, to = end, by = "days")) %>%
  mutate(day = ymd(day), weekDay = wday(day), weekNum = week(day)) %>% # get the relative week number
  mutate(weekNum = weekNum - (min(weekNum) - 1)) %>%
    filter(weekDay %in% c(2,4)) %>% # only keep Monday and Wednesday
      spread(key = weekDay, value = day) %>% # long to wide
        rename(Mon = `2`, Wed = `4`)

dates$content <- NA
## Holidays
dates$content[dates$Mon == ymd("2017-09-04")] <- "What's A Good Question (Labor Day)"
dates$content[dates$Mon == ymd("2017-11-20")] <- "Thanks Giving Break"
dates$content[dates$Mon == ymd("2017-12-11")] <- "Final Week"

dates$content[is.na(dates$content)] <- c("Being a Political Scientist", "Being A Scientist First!", "Where Does A Question Come From?", "What's A Concept?", "Let's Measure Politics!", "Measurement in Practice", "What's A Theory?", "Theory and Causal Inference", "Experimenting on Politics", "Principles of Case Study", "Case Study in Practice", "A Glance of Other Small-N Methods", "Understanding Large-N Analyses", "Professionalization")

weekList <- paste0("Week ", dates$weekNum, " (", dates$Mon, "/", dates$Wed, "): ", dates$content)
```

## `r weekList[1]`
This is the first week of our class.
As the beginning, you will read articles by two big names in political science.
They discuss what's political science and how to be a qualified political scientist. 
You are recommended to read Koehane (2009) first and then King (2006).
Try to find the answers to the following questions during your reading.

* According to Keohane, what's political science, and what's the crucial character of political scientists (and students in political science)? 
* What does inference mean in political science research? How are the so-called "descriptive" and "causal" inferences different from each other?
* Why should we care about reliability and validity of inferences?
* Why is experiment the best way to detect causal inferences?
* Do the standards in natural science fit political science? Why or why not?
* What's the way King suggests to start a research project? Why does he recommend it?
* Why does King emphasize to offer a minimal-change analysis before a fully-improved analysis in the replications?


## `r weekList[2]`
From this week, we formally start our journey towards being a political scientist.
The first step is to understand how political scientists (or social scientists in general) contribute to improving the insight into human society. 
The first part of Babbie discusses how social scientific inquiries are different from ordinary human inquiries and why they are important and valuable.
The second part of Babbie together with King's influential piece discusses the regular procedure (*please recall how important following a certain procedure is for political science research from last week.*) to conduct a valid and solid social science research. A quick note King (1995), the author tried to talk about every type of audience the piece might expose in "Proposed Solution," you are free to scan all of them, but please pay most attention to his suggestions to the "Authors."

Try to think about the following questions when you read the readings:

* How is scientific theory different from philosophy?
* What are the three main purposes of social research?
* Babbie discusses three dialects in social research, which one is the most important?
* In Babbie's discussion about how to design a research project, what's the relationship between theoretical and empirical blocks?
* According to King, what's the purpose to do replication and why it is important for political science?
* Why are we worrying ourselves with what might be called "duplication" of misting research? Isn't the more important question actual replication where the same measurements are applied to new substantive areas, countries, or time periods?

## `r weekList[3]`

The reading for this week is pretty long, isn't it---especially given that we only have one class? 
So, here are some good news:
first, despite its length, this is an excellent piece illustrating how to start from a general interest to a qualified political science research.
You would rarely find such a detailed illustration that elaborate every single step to build up a project in other research design articles (or even books)!
So, treat it not only as an introduction of political scientific inquiries but also a template that, when you don't know what or how to do the next step in your own project, go back to check *how Geddes did* and mimic her.
More than often, you will get some inspiration to get out of the mesh.
Second, regarding the week topic, you can pay most attention to the first 24 pages (pp.27--50) and scan the later 38 pages. 
In the class, we will also mostly focus on how the author narrows a big romantic question to a testable topic to examine.
I will briefly discuss the later sections to show how the question selection and research strategy affect the research design and empirical tests, but, again, our focus will still on the research question exploration and generalization.

When you read the chapter, try to find answers to the following questions:

* What is the mental preparation a scholar should make when they start a project?
* Why is it a bad idea to try to seek research questions directly from the existing literature?
* In Geddes' case, she also used literature several times, how do they differ from the method to use literature that she disagree?
* What's a model? How is it useful in the research question hunting?
* What's analytic narratives? How does it differ from Geddes' approach?
* How does Geddes disaggregate the large question?
* Why does Geddes focus on individuals to examine the topic of interest?

## `r weekList[4]`

We talked about what is a good question in political science in the last week.
We will continue this topic in this week and especially focus on how you can frame or refine a research question from a general interest and how to find a proper research strategy.
Babbie provides a clear review of the general purposes in social research and relevant strategies social scientists usually take to achieve these purposes.
Raign interprets the same topic in a different way and underscore some goals that are unique for social rather than natural science. 
When you read these pieces, try to think about the following questions:

* Babbie talked about three purposes of research. Can you give an example of each? Is there another purposes do you think a social research should aim?
* What's ecological fallacy? Why does ecological fallacy cause a problem giving social science focuses on patterns in the society rather than a single case? 
* What are cross-sectional and longitudinal studies? How are they different from each other?
* Ragin argued that one purpose of social science research is to "interpret culturally or historically significant phenomena." Then does social scientists do the same job as historians? 
* What are the relations among Ragin's seven goals of social research? 
* How does Ragin match the research strategies with the goals? (esp. Table 2.1) Are you convinced by this matching?


## `r weekList[5]`

In this week we learn how to conceptualize.
This is a step when you have found a research question and start to think about how to frame and present the primary components in it so that both you and your potential readers have an agreement on what your study is about.
Babbie discussed the basic principles of conceptualization, while most of his examples are quite sociological.
So, Collier and Levitsky's piece comes in to show you how a concept could be defined in a political research. 
Pay attention to the "ladder" illustration and see how one can use it to avoid invalid conceptualization.
Read through these materials and try to think about the following questions:

* How do you know a concept is valid?
* How is a conceptualization conducted? Which two components should be involved?
* What's "hermeneutic circle" of definition? How is that helpful for conceptualization?
* What's Satori's ladder? How does it help conceptualization?
* What's conceptual stretching? What's conceptual differentiation?


## `r weekList[6]`

In this week, we will start the first operationalization step: measuring abstract concepts.
Babbie discussed basic principles and several ways to build measurements.
Our task is not to be an expert on any of them but being exposed to all of them so that we know what we can do when we intend to do something.
Therefore, pay more attention to fundamental rules of measurements and the advantages and disadvantages of each measurement approach rather than the technical details.
One of the crucial concern of concept measurement is its validity. 
Babbie briefly discusses it and Adcock and Collier specify it in terms of political science.
In particular, they discussed a core concern in measurement validity: contextual specification.
Also, for now, you can just briefly scan their discussion about the typology of validation, unless you are interested.
They are helpful but involves reliability and precision mentioned in Babbie also as a type of measurement validation. 
Be careful not letting this typology mess up your understanding from Babbie.

Read through these materials and try to think about the following questions:

* How do you choose from the four measure types (nominal, ordinal, interval, and ratio)? What is the assumption you've made when you choose one of them?
* What's the relation among measurement precision, reliability, and accuracy?
* What steps should one go through to build an index?
* What is a "true" Likert scale?
* Why should scholars be concerned about contextual specification in building the measurements?
* What are the means for scholars to build contextual specified concepts?


## `r weekList[7]`
*Due for the research question approval: `r dates$Wed[7]`.*

Since this is the due week for your research question and the last week before the midterm, I only set one reading to save some of your time for the assignment and exam review. 
However, it does not suggest this piece is less important. 
Seawright and Collier provide a comprehensive yet succinct review of the common ways to measure democracy---one of the most important and complex concepts in political science.
You should think about to apply the approaches discussed in the article in your own works or evaluate the studies in the literature.

Read through the material and try to think about the following questions:

* What're "level of measurement" and  "case-based" traditions to measure concepts?
* Do the author have a preference of the four measurement traditions?
* Is it possible for a scholar to apply multiple approaches to measure a concept? If so, which approaches can they combine, and what are the benefit and cost for this mixed application?


<!-- ## `r weekList[8]` -->


<!-- ## `r weekList[9]` -->

<!-- ## `r weekList[10]` -->


<!-- ## `r weekList[11]` -->

<!-- ## `r weekList[12]` -->


<!-- ## `r weekList[13]` -->

<!-- *Due for the brief of the theory: `r dates$Mon[13]`.* -->

<!-- ## `r weekList[14]` -->

<!-- ## `r weekList[15]` -->


<!-- ## `r weekList[16]` -->

<!-- ## `r weekList[17]` -->
<!-- *Due for the research proposal: `r dates$Mon[17]`.* -->
