---
output: 
  bookdown::pdf_document2:
    keep_tex: true
    fig_caption: yes
    latex_engine: pdflatex
    template: D:/MEGAsync/Dropbox/07_usefulNotes/svm-latex-syllabus.tex
geometry: margin=1in

title: "POLI 2000: Designing Political Research"
author: Yue Hu
date: "Fall 2017"
email: "yue-hu-1@uiowa.edu"
#web: "svmiller.com/teaching"
officehours: "12:30 -- 15:30 M & by Appointment"
office: "313 Shaeffer Hall"
classroom: "105 EPB"
classhours: "15:30 -- 16:45 M/W"
fontsize: 11pt
biblio-style: ajps
bibliography: readings.bib
header-includes:
   - \linespread{1.05}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(pacman)
p_load(dotwhisker, ggplot2, interplot,# Visualization
       lubridate, RefManageR,# Applied
       # dependency
       readxl, haven, descr, stringi, stringr, arm, car, stargazer,
       broom, tidyverse) # data wrangling

set.seed(313)

# Bib setting
ajps_mimic <- RefManageR:::MakeBibLaTeX()
with(ajps_mimic,{
  ajps_mimic$fmtJournal <- function(s){
                                if (length(s$journaltitle)) {
                                    res <- emph(cleanupLatex(s$journaltitle))
                                    if (length(s$journalsubtitle))
                                        res <- paste(addPeriod(res), emph(cleanupLatex(s$journalsubtitle)))
                                    return(res)
                                }
                                else if (!is.null(s$journal)) {
                                    emph(cleanupLatex(s$journal))
                                }
     }
     
     ajps_mimic$fmtURL <- function (paper) {
        if (length(paper[["url"]])) {
            res <- paper$url
            res <- switch(docstyle, html = paste0("\\url{", 
                res, "}"), markdown = paste0("[", res, "](", 
                res, ")"), paste0("\\url{", res, "}"))
            if (length(paper$urldate)) {
                fDate <- try(ProcessDate(paper$urldate, NULL), TRUE)
                if (!is.null(fDate) && !inherits(fDate, "try-error")) 
                    res <- paste0(res, " (visited on ", DateFormatter(fDate, 
                      TRUE), ")")
            }
            addPeriod(res)
        }
        else if (length(paper$urldate)) {
            fDate <- try(ProcessDate(paper$urldate, NULL), TRUE)
            if (!is.null(fDate) && !inherits(fDate, "try-error")) 
                paste0("(Visited on ", DateFormatter(fDate, TRUE), 
                    ").")
        }
     }
     
     ajps_mimic$fmtLanguage <- function(lang) {
    if (length(lang) && tolower(lang) != "english") 
        paste0("[", sub("\\b(\\w)", "\\U\\1", lang, perl = TRUE, 
            useBytes = TRUE),"]")
       }
     
     ajps_mimic$formatArticle <- function (paper) {
    collapse(c(fmtPrefix(paper), fmtBAuthor(paper), fmtJTitle(paper$title), fmtLanguage(paper$language), 
        fmtAddOn(paper$titleaddon),
        fmtTranslator(paper), fmtCommentator(paper$commentator), 
        fmtAnnotator(paper$annotator), fmtVersion(paper$version), 
        sentenceP(paste0(c(paste0(c(fmtJournal(paper), fmtSeries(paper$series)), 
            collapse = ""), fmtVolume(paper$volume, paper$number), 
            fmtJournDate(paper)), collapse = " "), fmtBTitle(paper$issuetitle, 
            paper$issuesubtitle), fmtEditor(paper, suffix = NULL, 
            prefix = ". "), fmtNote(paper$note, prefix = ". ", 
            suffix = NULL), pgs = fmtPages(paper$pages, paper$pagination), 
            sep = ""),fmtURL(paper), fmtAddendum(paper$addendum), 
        fmtPubstate(paper$pubstate)))
     }
     
     ajps_mimic$formatArticle <- function (paper) {
    collapse(c(fmtPrefix(paper), fmtBAuthor(paper), fmtJTitle(paper$title), fmtLanguage(paper$language), 
        fmtAddOn(paper$titleaddon),
        fmtTranslator(paper), fmtCommentator(paper$commentator), 
        fmtAnnotator(paper$annotator), fmtVersion(paper$version), 
        sentenceP(paste0(c(paste0(c(fmtJournal(paper), fmtSeries(paper$series)), 
            collapse = ""), fmtVolume(paper$volume, paper$number), 
            fmtJournDate(paper)), collapse = " "), fmtBTitle(paper$issuetitle, 
            paper$issuesubtitle), fmtEditor(paper, suffix = NULL, 
            prefix = ". "), fmtNote(paper$note, prefix = ". ", 
            suffix = NULL), pgs = fmtPages(paper$pages, paper$pagination), 
            sep = ""),fmtURL(paper), fmtAddendum(paper$addendum), 
        fmtPubstate(paper$pubstate)))
     }
     
     ajps_mimic$formatUnpublished <- function (paper) {
        collapse(c(fmtPrefix(paper), fmtBAuthor(paper), fmtIBTitle(paper$title, 
            paper$subtitle, FALSE), fmtAddOn(paper$titleaddon), fmtLanguage(paper$language), 
            fmtHowPublished(paper$howpublished), fmtNote(paper$note), 
            sentence(fmtPublisher(NULL, paper$location, paper$address), sep = ""), fmtDOI(paper$doi), 
            fmtURL(paper), fmtAddendum(paper$addendum), fmtPubstate(paper$pubstate)))
     }
     
     ajps_mimic$formatMisc <- function (paper) {
    collapse(c(fmtPrefix(paper), fmtBAuthor(paper), fmtIBTitle(paper$title, 
            paper$subtitle, FALSE), fmtAddOn(paper$titleaddon), fmtLanguage(paper$language), 
        fmtEditor(paper, !length(paper$author)), fmtHowPublished(paper$howpublished), 
        addPeriod(fmtType(paper$type)), fmtVersion(paper$version), 
        fmtNote(paper$note), sentence(fmtPublisher(paper$organization, 
            paper$location, paper$address), fmtDate(attr(paper, 
            "dateobj")), sep = ""), fmtDOI(paper$doi), fmtEprint(paper), 
        fmtURL(paper), fmtAddendum(paper$addendum), fmtPubstate(paper$pubstate)))
}
})


tools::bibstyle("ajps_mimic", ajps_mimic)

bib <- ReadBib("readings.bib", check = FALSE)
BibOptions(check.entries = FALSE, 
           first.inits = FALSE,
           bib.style = "ajps_mimic",
           style = "latex",
           max.names = 4,
           dashed = FALSE,
           sorting = "ydnt")
```


# Overview
How do candidates win elections? 
Why do countries get involved in international crises and wars? 
What makes a country more powerful than the others?
What explains the choices of violent non-state actors like terrorists? 
There are just some of the questions that political scientists study. 
The goal of this course is to show you how to research these questions as a scholar in political science.
This course will introduce students to political science research and various ways that social scientific research is undertaken.

This class will introduce the core elements of a political science research, such as concept, theory, hypothesis, and evidence. 
You will also learn how to build a new theory, develop testable causal inferences, and design different approaches to test your theories empirically. 
Emphasis will be on an active hands-on learning environment and fully interactions between the instructor and students. 
Students can expect to comprehend the research produced in Political Science and learn to conduct their own.

# Requirements
I will base your grade for the course on your performance in the four areas below. 
You will get a score for each component, and your total grade will be the sum of them. 
The grade points will be translated to letter grades in the following way:
93-100 A, 90-92.9 A-, 87-89.9 B+, 83-86.9 B, 80-82.9 B-, 77-79.9 C+, 73-76.9 C, 70-72.9 C-,
67-69.9 D+, 63-66.9 D, 60-62.3 D-, 59.9 or less F.

```{r calendar, include=FALSE}
# Opening Date: 2017-08-21 ####
start <- ymd("2017-08-21")
# Final Week: 2017-12-11 ####
end <- ymd("2017-12-17")

dates <- data.frame(day = seq(from = start, to = end, by = "days")) %>%
  mutate(day = ymd(day), weekDay = wday(day), weekNum = week(day)) %>% # get the relative week number
  mutate(weekNum = weekNum - (min(weekNum) - 1)) %>%
    filter(weekDay %in% c(2,4)) %>% # only keep Monday and Wednesday
      spread(key = weekDay, value = day) %>% # long to wide
        rename(Mon = `2`, Wed = `4`)

dates$content <- NA
## Holidays
dates$content[dates$Mon == ymd("2017-09-04")] <- "What's A Good Question (Labor Day)"
dates$content[dates$Mon == ymd("2017-11-20")] <- "Thanks Giving Week"
dates$content[dates$Mon == ymd("2017-12-11")] <- "Final Week"

dates$content[is.na(dates$content)] <- c("Being a Political Scientist", "Being Scientific", "How to Find Research Question", "Concepts", "Principles of Measurement", "Measurement in Practice", "What's Theory?", "Theory and Causal Inference", "Experimental Logic and Design", "Principles of Case Study", "Case Study in Practice", "A Glance of Other Small-N Methods", "Understanding Large-N Analyses", "Professionalization")

weekList <- paste0("Week ", dates$weekNum, " (", dates$Mon, "/", dates$Wed, "): ", dates$content)
```


## Class Performance (10% attendance + 10% participation + 5% presentation). 

I will take attendance at the begining of every class. Every attendence is marked as one score.
You are given three (free) absences (i.e. I don’t need, nor do I want, an excuse) but any absences beyond that will result in one score reduction per absence regardless of the excuse, except for medical reasons. 
Further, sports, music, Greek and other events are not “excusable” absences.
You should use your free absences for these events. 
The ratio of your attendence score to the total number of the class minus 3 will determine how much you will get from the 10% attendence grade.
Confused? Come see me sooner rather than later if you need clarification of this policy.   

Regarding participation, I am looking for you to show that you have fully read and critically evaluated the assigned readings (all available in ICON) and are actively engaged in our in-class discussions.
Before each week's class you will receive a one-page reading guideline.
It will give you a hint how to read the week's readings and which part you should pay special attention to. 
The guideline will always include a recommended reading order and several questions to help you comprehend the materials.
I will provide a “tentative” participation grade prior to the Fall Break so you have an idea of whether you need to improve your level of participation before final grades are given.

By the second week, we will decide a presentation schedule together. 
You will sign in a schedule sheet by picking the topic and articles you are interested.
Starting from the third Monday, every first 20 minutes will be your show time.
The student who signed for that day will make a 10-min presentation about the reading.
The presentation should include three parts: a brief summarising what the article is about and its relations with other materials, which point in the article impresses you the most and why, and at least one question you really want to know but the article does not spell it out. 
I will evaluate your performance in each---especially the latter two---aspects (see more details in the attached rubric).
Please cherish this chance to practice your presentation capability, and there is no chance for make-up presentation if you miss it. 

## In-Class Quizzes (10%)
You will get ten pop quizzes throughout the semester. 
Each quiz includes 2-3 questions about the required readings we are going to discuss in the class.
(Hint: some questions may come from the reading guide.)
At the end of the semester, the eight highest scores of the ten quizzes will be recorded to contribute to your final grade.
Quizzes will be administered and completed either at the beginning or the end of class. 
You cannot make up any missed or failed quizzes for any reason.
Feel free to discuss the readings with your classmates prior to class. 
*However, you cannot share your answers to the reading questions with your classmates.*

## Critical Response Paper (12%)

You are expected to submit two response papers over the course of the semester. 
These must be from two different weeks and must be submitted before the week begins.
(You are free to write one response paper for your presentation week.)
In the paper, You need to review at least three reading materials of the week.
Moreover, I would like to see

1. One and ONLY one paragraphs to summarize each material.
1. Some discussion about what do you learn from these materials relating to the weekly topic.
1. Your perspective on the argument in the materials---do you agree with the author? If yes, why are his/her arguments convincing for you? If not, why?
1. Cite other sources if appropriate (but not required).


The paper is due at the BEGINNING of the Monday class (i.e., 15:30) of the week the materials are going to discussed (submit to ICON). 
Late paper will be penalized 10 points for each day of being late. 
Each paper should be 2-4 pages, double-spaced, 1-inch margins, and in 12 font size.
Papers will be evaluated based on the above points (see more details in the attached rubric).



## Examination (20%)
There is only one exam (viz. midterm) for this course.
The exam is comprised of identification and short essay questions.
The exam will be held on 2017-10-09 in the same class of the lecture.


## Research Proposal (23%)
You are expected to submit a research proposal at the end of the semester.
It could be a proposal for your degree thesis or for a funding application.
The proposal should include at least six parts:

1. A cover table (see the template on ICON).
1. An introduction to your research question and why it is important.
1. A brief literature review about what scholars have done on this topic. You need to cite at least three articles published in academic journals of political science in this part and discuss how they relate to your topic. Your citation should be in the style used by the American Political Science Association (see the guideline [here](http://www.apsanet.org/portals/54/Files/Publications/APSAStyleManual2006.pdf)).
1. A section discussing your theory and hypotheses.
1. A section discussing the data and method you plan to use to test your theory and why they are the best choice for your project.
1. A section discussing the operational feasibility of your research design.

The proposal is expected  5-10 pages (excluding the title and reference pages) in double-spaced, 1-inch margins, and 12 font size.
The proposal will be evaluated based on each of the above parts and the overall writing  (see more details in the attached rubric).

Here are some important dates relating to the research proposal:

* You must get your research question approved by the instructor by `r dates$Wed[7]` (submitted in ICON).
* You must submit a brief about your theory by `r dates$Mon[13]` (submitted in ICON).
* The proposal is due by `r dates$Mon[17]`. Late paper will be penalized 30 points for each day of being late (submitted in ICON). 

## Extra credit
I offer 5 extra credits that can be directly contributed to your final grade (1 extra credit = 1 score of the grade).
There are three ways to get extra credits. 

1. You can earn 2 extra credits by using bibliography management software (EndNote, Jabref, Zotero, etc. see more information about this type of software [here](https://en.wikipedia.org/wiki/Comparison_of_reference_management_software).) and submit relevant bibliography files with your proposal.

1. You can earn 2 credits by gaining a Certification in Human Subjects Protections (CITI) in "Group 2 - Social & Behavioral - IRB-02". See more information about it [here](https://hso.research.uiowa.edu/certifications-human-subjects-protections-citi). To get the credit, you need to send the CITI proof to me by the due of the research paper.

1. You can get 1 extra credit by attending an academic workshop held by the Department of Political Science and send me a selfie at the workshop scene.


# Required textbook:
```{r, results = "asis"}
bib[c("Babbie2012", "VanEvera1997")]
```


# Schedule
## `r weekList[1]`
```{r, results = "asis"}
bib[c("Dryzek2006", "Keohane2009", "King2006")]
```

## `r weekList[2]`
@Babbie2012, pp.1-27, 112-120.

```{r, results = "asis"}
bib[c("Almond1988", "King1995"， "Lakatos1970")]
```

## `r weekList[3]`
```{r, results = "asis"}
bib["Geddes2010"]
```

@VanEvera1997, pp.97-99.

## `r weekList[4]`
@Babbie2012, pp.91-112.

```{r, results = "asis"}
bib[c("McKeown1999", "Perez2017")]
```

```{r, results = "asis"}
bib[c("Ragin2010")]
```
(Chapter 1, 2)

## `r weekList[5]`
@Babbie2012, pp.165-177.

```{r, results = "asis"}
bib[c("Sartori1970", "Collier1993", "Collier1997", "Barnett2005")]
```

## `r weekList[6]`
@Babbie2012, pp.177-194, 197-223.

```{r, results = "asis"}
bib[c("Adcock2001","Seawright2014", "Schedler2012", "Treier2008")]
```


## `r weekList[7]`
*Due for the research question approval: `r dates$Wed[7]`.*

@VanEvera1997, pp.7-50.
Midterm Review

## `r weekList[8]`
Midterm.

@Babbie2012, pp.57-83.

```{r, results = "asis"}
bib[c("Gerring2005", "Przeworski1970")]
```
Chapter 1.

## `r weekList[9]`

```{r, results = "asis"}
bib[c("Gerring2010", "Fearon1991", "Bernstein2000", "Johnson2002")]
```

## `r weekList[10]`

@Babbie2012, pp.271-291.

```{r, results = "asis"}
bib[c("Mintz2004", "Gerber2011", "Mintz2006")]
```

## `r weekList[11]`

```{r, results = "asis"}
bib[c("Gerring2004", "Levy2008", "McKeown2004")]
```

```{r, results = "asis"}
bib[c("Przeworski1970")]
```
31-39, 74-87.


## `r weekList[12]`

@VanEvera1997, pp.49-88.

```{r, results = "asis"}
bib[c("Geddes1990", "Bennett2007", "Munck2004")]
```

## `r weekList[13]`

*Due for the brief of the theory: `r dates$Mon[13]`.*

@Babbie2012, pp.295-321.

```{r, results = "asis"}
bib[c("Geertz1994", "Capoccia2007", "Bennett2008")]
```

## `r weekList[14]`

## `r weekList[15]`

@Babbie2012, pp.415-438.

```{r, results = "asis"}
bib[c("Tang2016", "Hafner-Burton2006", "Mahoney2006")]
```

## `r weekList[16]`

@Babbie2012, pp.498-519.

@VanEvera1997, pp.99-111.


[Presentation at APSA 2014: Policy Bargaining and International Conflict](https://www.youtube.com/watch?v=bwNBXuz2eRg)

[Presentation at MPSA 2017: Trump Scenes](https://www.youtube.com/watch?v=Z4ISkF2H4tk)

## `r weekList[17]`
*Due for the research proposal: `r dates$Mon[17]`.*


\clearpage

# Rubric for In-Class Presentation

| Item                          | Criterion                                                                                                                                         | Grade |
|-------------------------------|--------------------------------------------------------------------------------------------------------------------------------------------------|-------|
| Duration                      | > 8 mins 1; 5-8 mins .5; < 5 min 0.                                                                                                               | X     |
| Summary about the material       | clearly described the logic and main arguments 1; covered the main arguments 0.5; failed to capture the main arguments 0.                         | X     |
| Relation with other materials | clearly explained the relation with the week topic and other materials 1; mention another material 0.5; only talked about the assigned reading 0. | X     |
| Impressive point              | clearly described the impressive point and explained why 1; mentioned the impressive point 0.5; not discuss the point at all 0.                   | X     |
| Critical reading              | clearly described the question and why it's important 1; posted a question 0.5; not raise any question 0.                                         | X     |                                                   |       |

# Rubric for Response Paper

| Item                    | Criterion                                                                                                                      | Grade |
|-------------------------|-------------------------------------------------------------------------------------------------------------------------------|-------|
| Summary of the material | clearly described the logic and main arguments 2; covered the main arguments 1; failed to capture the main arguments 0        | X     |
| learned Point            | clearly explained the learned points and their importance 2; clearly describe the points learned 1; no learned point mentioned 0 | X     |
| Critical thinking       | clearly opinions and why 2; have a perspective of the reading 1; no perspective at all 0                                      | X     |


\clearpage

# Rubric for the Research Proposal

| Item                            | Criterion                                                                                                                                                                                                            | Grade |
|---------------------------------|---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|-------|
| Cover table (5%)                | Is the table fully filled? Is every element defined?                                                                                                                                                                | X     |
| Research Question Approval (5%) | Was the research proposal approved by 2017-10-09?                                                                                                                                                                   | X     |
| Brief of Theory (5%)            | Was the brief of the theory submitted by 2017-11-12?                                                                                                                                                                | X     |
| Introduction (10%)              | Is the research question well stated? Does the intro clearly explain the importance of the study? Does the intro clearly explain the potential contribution of this project?                                        | X     |
| Literature Review (10%)         | Does the LR address more than three existing studies? Does the LR clearly review the findings of the existing literature? Does the LR clearly state how the existing literature serve as the basis for this study?   | X     |
| Theory (15%)                    | Is the causal logic clearly stated? Are the concepts in the theory well defined? Is the causal chain complete and consistent? Are the causal inferences (hypotheses) clearly stated and consistent with the theory? | X     |
| Research Design (20%)           | Does the author clearly describe the strategy to test the hypotheses? Does the author well defend his/her method choice?                                                                                            | X     |
| Data (10%)                      | Is there a complete plan of data collection? How do the data fit the research design? Validations?                                                                                                                   | X     |
| Feasibility (5%)                | Is the research design a feasible one for a college student? What're the potential difficulties the researcher may encounter?                                                                                         | X     |
| Citation (5%)                   | Are the citations well presented? Is there a full bibliography attached? Are the citation and bibliography styles consistent with the APSR requirement?                                                             | X     |
| Overall writing (10%)           | Does the language well edited? Do the paragraphs well framed and organized? Does the layout match the requirement?                                                                                                  | X     |


\clearpage

# CLAS Teaching Policies & Resources — Syllabus Insert
## Administrative Home
The College of Liberal Arts and Sciences is the administrative home of this course and governs matters such as the add/drop deadlines, the second-grade-only option, and other related issues. Different colleges may have different policies. Questions may be addressed to 120 Schaeffer Hall, or see the CLAS Academic Policies Handbook at https://clas.uiowa.edu/students/handbook.

## Electronic Communication
University policy specifies that students are responsible for all official correspondences sent to their University of Iowa e-mail address (@uiowa.edu). Faculty and students should use this account for correspondences ([Operations Manual, III.15.2](https://opsmanual.uiowa.edu/human-resources/professional-ethics-and-academic-responsibility#15.2), k.11).

## Accommodations for Disabilities
The University of Iowa is committed to providing an educational experience that is accessible to all students. A student may request academic accommodations for a disability (which includes but is not limited to mental health, attention, learning, vision, and physical or health-related conditions). A student seeking academic accommodations should first register with Student Disability Services and then meet with the course instructor privately in the instructor's office to make particular arrangements. Reasonable accommodations are established through an interactive process between the student, instructor, and SDS. See https://sds.studentlife.uiowa.edu/ for information. 

## Nondiscrimination in the Classroom
The University of Iowa is committed to making the classroom a respectful and inclusive space for all people irrespective of their gender, sexual, racial, religious or other identities. Toward this goal, students are invited to optionally share their preferred names and pronouns with their instructors and classmates. The University of Iowa prohibits discrimination and harassment against individuals on the basis of race, class, gender, sexual orientation, national origin, and other identity categories set forth in the University’s Human Rights policy. For more information, contact the Office of Equal Opportunity and Diversity, diversity@uiowa.edu, or visit [diversity.uiowa.edu](https://diversity.uiowa.edu/office/equal-opportunity-and-diversity).

## Academic Honesty
All CLAS students or students taking classes offered by CLAS have, in essence, agreed to the [College's Code of Academic Honesty](https://clas.uiowa.edu/students/handbook/academic-fraud-honor-code): "I pledge to do my own academic work and to excel to the best of my abilities, upholding the [IOWA Challenge](https://newstudents.uiowa.edu/iowa-challenge). I promise not to lie about my academic work, to cheat, or to steal the words or ideas of others; nor will I help fellow students to violate the Code of Academic Honesty." Any student committing academic misconduct is reported to the College and placed on disciplinary probation or may be suspended or expelled ([CLAS Academic Policies Handbook](https://clas.uiowa.edu/students/handbook)).

## CLAS Final Examination Policies
The final examination schedule for each class is announced by the Registrar generally by the fifth week of classes. Final exams are offered only during the official final examination period. No exams of any kind are allowed during the last week of classes. All students should plan on being at the UI through the final examination period. Once the Registrar has announced the date, time, and location of each final exam, the complete schedule will be published on the Registrar's web site and will be shared with instructors and students. It is the student's responsibility to know the date, time, and place of a final exam.

## Making a Suggestion or a Complaint
Students with a suggestion or complaint should first visit with the instructor (and the course supervisor), and then with the departmental DEO. Complaints must be made within six months of the incident ([CLAS Academic Policies Handbook](https://clas.uiowa.edu/students/handbook)).

## Understanding Sexual Harassment
Sexual harassment subverts the mission of the University and threatens the well-being of students, faculty, and staff. All members of the UI community have a responsibility to uphold this mission and to contribute to a safe environment that enhances learning. Incidents of sexual harassment should be reported immediately. See the UI [Office of the Sexual Misconduct Response Coordinator](https://osmrc.uiowa.edu/) for assistance, definitions, and the full University policy.

## Reacting Safely to Severe Weather
In severe weather, class members should seek appropriate shelter immediately, leaving the classroom if necessary. The class will continue if possible when the event is over. For more information on Hawk Alert and the siren warning system, visit the [Department of Public Safety website](https://police.uiowa.edu/emergency-communications).


\clearpage

# Reference
