---
output: 
  bookdown::pdf_document2:
    keep_tex: true
    fig_caption: yes
    latex_engine: pdflatex
    template: D:/MEGAsync/Dropbox/07_usefulNotes/svm-latex-syllabus.tex
geometry: margin=1in

title: "POLI 2000: Designing Political Research"
author: Yue Hu
date: "Fall 2017"
email: "yue-hu-1@uiowa.edu"
web: uiowa.instructure.com/courses/65855
officehours: "12:30 -- 15:30 M & by Appointment"
office: "313 Shaeffer Hall"
classroom: "105 EPB"
classhours: "15:30 -- 16:45 M/W"
fontsize: 11pt
biblio-style: ajps
bibliography: readings.bib
header-includes:
   - \linespread{1.05}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(pacman)
p_load(dotwhisker, ggplot2, interplot,# Visualization
       lubridate, RefManageR,# Applied
       # dependency
       readxl, haven, descr, stringi, stringr, arm, car, stargazer,
       broom, tidyverse) # data wrangling

set.seed(313)

# Bib setting
ajps_mimic <- RefManageR:::MakeBibLaTeX()
with(ajps_mimic,{
  ajps_mimic$fmtJournal <- function(s){
                                if (length(s$journaltitle)) {
                                    res <- emph(cleanupLatex(s$journaltitle))
                                    if (length(s$journalsubtitle))
                                        res <- paste(addPeriod(res), emph(cleanupLatex(s$journalsubtitle)))
                                    return(res)
                                }
                                else if (!is.null(s$journal)) {
                                    emph(cleanupLatex(s$journal))
                                }
     }
     
     ajps_mimic$fmtURL <- function (paper) {
        if (length(paper[["url"]])) {
            res <- paper$url
            res <- switch(docstyle, html = paste0("\\url{", 
                res, "}"), markdown = paste0("[", res, "](", 
                res, ")"), paste0("\\url{", res, "}"))
            if (length(paper$urldate)) {
                fDate <- try(ProcessDate(paper$urldate, NULL), TRUE)
                if (!is.null(fDate) && !inherits(fDate, "try-error")) 
                    res <- paste0(res, " (visited on ", DateFormatter(fDate, 
                      TRUE), ")")
            }
            addPeriod(res)
        }
        else if (length(paper$urldate)) {
            fDate <- try(ProcessDate(paper$urldate, NULL), TRUE)
            if (!is.null(fDate) && !inherits(fDate, "try-error")) 
                paste0("(Visited on ", DateFormatter(fDate, TRUE), 
                    ").")
        }
     }
     
     ajps_mimic$fmtLanguage <- function(lang) {
    if (length(lang) && tolower(lang) != "english") 
        paste0("[", sub("\\b(\\w)", "\\U\\1", lang, perl = TRUE, 
            useBytes = TRUE),"]")
       }
     
     ajps_mimic$formatArticle <- function (paper) {
    collapse(c(fmtPrefix(paper), fmtBAuthor(paper), fmtJTitle(paper$title), fmtLanguage(paper$language), 
        fmtAddOn(paper$titleaddon),
        fmtTranslator(paper), fmtCommentator(paper$commentator), 
        fmtAnnotator(paper$annotator), fmtVersion(paper$version), 
        sentenceP(paste0(c(paste0(c(fmtJournal(paper), fmtSeries(paper$series)), 
            collapse = ""), fmtVolume(paper$volume, paper$number), 
            fmtJournDate(paper)), collapse = " "), fmtBTitle(paper$issuetitle, 
            paper$issuesubtitle), fmtEditor(paper, suffix = NULL, 
            prefix = ". "), fmtNote(paper$note, prefix = ". ", 
            suffix = NULL), pgs = fmtPages(paper$pages, paper$pagination), 
            sep = ""),fmtURL(paper), fmtAddendum(paper$addendum), 
        fmtPubstate(paper$pubstate)))
     }
     
     ajps_mimic$formatArticle <- function (paper) {
    collapse(c(fmtPrefix(paper), fmtBAuthor(paper), fmtJTitle(paper$title), fmtLanguage(paper$language), 
        fmtAddOn(paper$titleaddon),
        fmtTranslator(paper), fmtCommentator(paper$commentator), 
        fmtAnnotator(paper$annotator), fmtVersion(paper$version), 
        sentenceP(paste0(c(paste0(c(fmtJournal(paper), fmtSeries(paper$series)), 
            collapse = ""), fmtVolume(paper$volume, paper$number), 
            fmtJournDate(paper)), collapse = " "), fmtBTitle(paper$issuetitle, 
            paper$issuesubtitle), fmtEditor(paper, suffix = NULL, 
            prefix = ". "), fmtNote(paper$note, prefix = ". ", 
            suffix = NULL), pgs = fmtPages(paper$pages, paper$pagination), 
            sep = ""),fmtURL(paper), fmtAddendum(paper$addendum), 
        fmtPubstate(paper$pubstate)))
     }
     
     ajps_mimic$formatUnpublished <- function (paper) {
        collapse(c(fmtPrefix(paper), fmtBAuthor(paper), fmtIBTitle(paper$title, 
            paper$subtitle, FALSE), fmtAddOn(paper$titleaddon), fmtLanguage(paper$language), 
            fmtHowPublished(paper$howpublished), fmtNote(paper$note), 
            sentence(fmtPublisher(NULL, paper$location, paper$address), sep = ""), fmtDOI(paper$doi), 
            fmtURL(paper), fmtAddendum(paper$addendum), fmtPubstate(paper$pubstate)))
     }
     
     ajps_mimic$formatMisc <- function (paper) {
    collapse(c(fmtPrefix(paper), fmtBAuthor(paper), fmtIBTitle(paper$title, 
            paper$subtitle, FALSE), fmtAddOn(paper$titleaddon), fmtLanguage(paper$language), 
        fmtEditor(paper, !length(paper$author)), fmtHowPublished(paper$howpublished), 
        addPeriod(fmtType(paper$type)), fmtVersion(paper$version), 
        fmtNote(paper$note), sentence(fmtPublisher(paper$organization, 
            paper$location, paper$address), fmtDate(attr(paper, 
            "dateobj")), sep = ""), fmtDOI(paper$doi), fmtEprint(paper), 
        fmtURL(paper), fmtAddendum(paper$addendum), fmtPubstate(paper$pubstate)))
}
})


tools::bibstyle("ajps_mimic", ajps_mimic)

bib <- ReadBib("readings.bib", check = FALSE)
BibOptions(check.entries = FALSE, 
           first.inits = FALSE,
           bib.style = "ajps_mimic",
           style = "latex",
           max.names = 4,
           dashed = FALSE,
           sorting = "ydnt")
```


# Overview
How do candidates win elections? 
Why do countries get involved in international crises and wars? 
What makes a country more powerful than the others?
What explains the choices of violent non-state actors like terrorists?
There are just some of the questions that political scientists study. 
The goal of this course is to show you how to research these questions as a scholar in political science.
This course will introduce students to political science research and various ways that social scientific research is undertaken.

## Objectives

This class will introduce core elements of political science research, such as concept, theory, hypothesis, and evidence. 
You will also learn how to develop a new theory, construct testable causal inferences, and design different approaches to test your theories empirically. 
Emphasis will be on an active hands-on learning environment and full interaction between the instructor and students. 

There are three fundamental goals of this course.
First, students are expected to understand the basic principles of scientific research and apply them to evaluate the established or on-going projects in political science.
Second, students are expected to understand common methods in political science research and how they can offer empirical evidence to test theoretical inferences.
Third, by taking the course, students are expected to be able to develop their own research designs following the principles of social science research. 

# Requirements
I will base your grade for the course on your performance in the four areas below. 
You will get a score for each component, and your total grade will be the sum of them. 
The grade points will be translated to letter grades in the following way:
93-100 A, 90-92.9 A-, 87-89.9 B+, 83-86.9 B, 80-82.9 B-, 77-79.9 C+, 73-76.9 C, 70-72.9 C-,
67-69.9 D+, 63-66.9 D, 60-62.3 D-, 59.9 or less F.

```{r calendar, include=FALSE}
# Opening Date: 2017-08-21 ####
start <- ymd("2017-08-21")
# Final Week: 2017-12-11 ####
end <- ymd("2017-12-17")

dates <- data.frame(day = seq(from = start, to = end, by = "days")) %>%
  mutate(day = ymd(day), weekDay = wday(day), weekNum = week(day)) %>% # get the relative week number
  mutate(weekNum = weekNum - (min(weekNum) - 1)) %>%
    filter(weekDay %in% c(2,4)) %>% # only keep Monday and Wednesday
      spread(key = weekDay, value = day) %>% # long to wide
        rename(Mon = `2`, Wed = `4`)

dates$content <- NA
## Holidays
dates$content[dates$Mon == ymd("2017-09-04")] <- "What's A Good Question (Labor Day)"
dates$content[dates$Mon == ymd("2017-11-20")] <- "Thanksgiving Break"
dates$content[dates$Mon == ymd("2017-12-11")] <- "Final Week"

dates$content[is.na(dates$content)] <- c("Being a Political Scientist", "Being A Scientist First!", "Where Does A Question Come From?", "What's A Concept?", "Let's Measure Politics!", "Measurement in Practice", "What's A Theory?", "Theory and Causal Inference", "Experimenting on Politics", "Principles of Case Study", "Case Study in Practice", "A Glance of Other Small-N Methods", "Understanding Large-N Analyses", "Professionalization")

weekList <- paste0("Week ", dates$weekNum, " (", dates$Mon, "/", dates$Wed, "): ", dates$content)
```


## Class Performance (10% attendance + 10% participation + 5% presentation). 

I will take attendance at the beginning of every class. 
You are given three (free) absences (i.e., no excuse is needed), but any absences beyond that will result in ONE WHOLE GRADE REDUCTION per absence regardless of the excuse, except for serious medical reasons or participating in University-sponsored events.
Further, if you are part of any University-sponsored event that may cause more than three absences, you should let me know at least 24 hours before the fourth absence and show me the verification that you are the formal or necessary participant of the event. 
Non-University sponsored events are not excusable absences. 
You should use your free absences for them.
The ratio of the times of your attendance to the total number of the classes minus three will determine how much you will get from the 10% attendance grade.
If the ratio is equal or above one, you will get full 10% attendance grade.
Confused? Come see me sooner rather than later if you need clarification of this policy.   

Regarding participation, I am looking for you to show that you have fully read and critically evaluated the assigned readings (all selected articles and chapters outside the textbooks are available in the [Modules tab of ICON](https://uiowa.instructure.com/courses/65855/modules)) and are actively engaged in our in-class discussions.
Before each week's class, you will a quick reading guideline in ICON including some summaries and questions (also in the [Modules]((https://uiowa.instructure.com/courses/65855/modules))).
Hope it can give you a hint about how to read the week's readings and to which part you should pay special attention. 

```{r signUp, eval = FALSE}
sheet <- data.frame(day = seq(from = start, to = end, by = "days")) %>%
  mutate(day = ymd(day), weekDay = wday(day)) %>% # get the relative week number
    filter(weekDay %in% c(2,4)) 

sheet <- sheet[-c(1, 2, 3, 4, 5, 27, 28, 33, 34),]
sheet <- sheet[-c(24,25),] # omit the last week

sheet <- select(sheet, -weekDay) %>%
  mutate(content = c("Geddes 2010", 
  "Babbie 2016", "Ragin&Amoroso 2010",
  "Babbie 2016", "Collier&Levitsky 1997",
  "Babbie 2016", "Adcock&Collier2001",
  "Seawright 2014", 
  "MIDTERM REVIEW", "MIDTERM EXAM", 
  "Babbie 2016", 
  "Gerring 2005", "Fearon 1991",
  "Babbie 2016", "Gerber&Green 2011",
  "Gerring 2004", "Przeworski&Teune 1970",
  "Geddes 2010", "Bennett&Elman 2007",
  "Babbie 2016 (307-48)", "Babbie 2016 (382-408)",
  "Babbie 2016", "Tang et al. 2016"), 
  pre1 = NA, pre2 = NA)

sheet[9, ]$pre1 <- sheet[9, ]$pre2 <- sheet[10, ]$pre1 <- sheet[10, ]$pre2 <- "N/A"

names(sheet) <- c("Date", "Material", "Presentation 1", "Presentation 2")

data.table::fwrite(sheet, file = "signUp.csv")
```


An important part of class performance is in-class presentation.
By the second week, we will decide a presentation schedule. 
In each class day following, we will have two of you to share your thoughts on a required reading for a given day.
(In the following schedule, you will usually see two reading materials for each week.
The Monday presenters are required to focus on the first materia, and the Wednesday presenters should focuses on the second one.
For Week 13, the reading materials come from the same source, I've separated the readings for the presenters and marked them in the Schedule section.)
You can sign up for the date to present in the [course calendar ](https://uiowa.instructure.com/calendar#view_name=scheduler&view_start=2017-08-30&appointment_group_id=195)(ICON-Calendar-In-Class Presentation-Click the date-Reserve).
Starting from the third Wednesday (`r dates[3,"Wed"]`), every first 10 minutes will be your showtime.
The students who sign for same day are expected work together to prepare and conduct the presentation.
The presentation is expected to include three parts: (1) a quick summary of the article and its relations with other materials, (2) which point in the article impresses you the most and why, and (3) at least one question you really want to know but the article does not spell it out. 
I will evaluate your performance in each---especially the latter two---aspects (see more details in [Rubric for In-Class Presentation]).
*There is no chance for makeup presentation if you miss it.* 

## In-Class Quizzes (15%)
You will get eight pop quizzes throughout the semester. 
Each quiz includes 1-2 questions about the readings of the given *week*.
(Hint: some questions may come from the reading guideline.)
The six highest scores of them will contribute to your final grade.
Quizzes will be administered and completed at the beginning of class. 
*You cannot make up any missed or failed quizzes for any reason.*
Feel free to discuss the readings with your classmates before class. 
However, you cannot share your answers to the reading questions with your classmates.

## Critical Response Paper (10%)

You are expected to submit one response paper over the course of the semester. 
In the paper, You need to review at least two reading materials of a given week.
(You are free to write one response paper for your presentation week. The only prohibited week for response is `r weekList[16]`.)
Moreover, I would like to see:

1. One and ONLY one paragraph to summarize each material (article or assigned chapter).
1. Some discussion about what you learn from these materials relating to the weekly topic.
1. Discussing how the target materials relates to others in the given week.
1. Your perspective on the argument in the materials---do you agree with the authors? If yes, why are their arguments convincing for you? If not, why?

The paper should be 500-1000 words.
It will be graded on a 10 scale and evaluated based on the above points (see more details in [Rubric for Critical Response Paper]).
The paper is due at the BEGINNING of the Monday class (i.e., 15:30) of the week the materials are going to discussed (submit to ICON). 
Late paper will be penalized 1/10 of the total grade for each day it is late.


## Examination (20%)
There is only one exam (viz. midterm) for this course.
The exam is comprised of identification and short essay questions.
The exam will be held on 2017-10-09 at the same time as the regular lecture.


## Research Proposal (25%)
You are required to submit a research proposal by the end of the semester.
You could write it for your degree thesis or a funding application.
The proposal is expected to include at least six parts:

1. A cover page (see the [template on ICON](https://uiowa.instructure.com/courses/65855/files/4424694?module_item_id=1468917)).
1. An introduction to your research question and why it is important.
1. A brief literature review about what scholars have done on this topic. You need to cite at least three articles published in academic journals in political science and discuss how they relate to your topic. Your citation should be in the style used by the American Political Science Association (see the [guideline](http://www.apsanet.org/portals/54/Files/Publications/APSAStyleManual2006.pdf)).
1. A section discussing your theory and hypotheses.
1. A section discussing the data and method you plan to use for testing your theory and why they are the best choice for your project.
1. A section discussing the operational feasibility of your research design.

Each part is worth a proportion of total grade.
(See the grade distribution in [Rubric for Research Proposal]).
You will finish the project throughout the semester with my help. 
Here is the general plan and some important dates:

* You have half of the semester prior to the Midterm to figure out what **question** you want to study. Once you find it, submit it to ICON, and I will assess whether it is a good question for the proposal. You must get the research question approved by `r dates$Wed[7]`. Late submission will be penalized 1/5 of the section for each day of being late. 
* After (or even before) your research question selection, you should start reviewing the existing literature and construct the **theoretical arguments** about it. You must submit a brief (a couple of paragraphs) about the theory for my approval by `r dates$Mon[13]` (submitted in ICON). Late submission will be penalized 1/5 of the section for each day of being late. 
* The **final proposal** is due by `r dates$Mon[17]` (submitted in ICON). Late paper will be penalized 10/100 of the total grade for each day of being late. 


The proposal is expected to be 1500 - 2500 words (excluding the title and reference pages) in double-spaced, 1-inch margins, and 12 font size.
The proposal will be evaluated based on each of the above parts and the overall writing quality (see more details in [Rubric for Research Proposal]).

## Extra Credits
I offer five extra credits that can be directly contributed to your final grade (1 extra credit = 1 score of the grade).
There are two ways to get extra credits. 

1. You can earn three extra credits by using bibliography management software (EndNote, Jabref, Zotero, etc. See more information about this type of software [here](https://en.wikipedia.org/wiki/Comparison_of_reference_management_software).) and submitting relevant bibliography files with your proposal.

1. You can earn two credits by gaining a Certification in Human Subjects Protections (CITI) in "Group 2 - Social & Behavioral - IRB-02". See more information [here](https://hso.research.uiowa.edu/certifications-human-subjects-protections-citi). To get the credits, you need to send the CITI proof to me by the due of the research paper.


# Required Textbook
```{r, results = "asis"}
bib[c("Babbie2016")]
```


# Schedule
## `r weekList[1]`
```{r, results = "asis"}
bib[c("Keohane2009", "King2006")]
```

## `r weekList[2]`
@Babbie2016, pp.4--28, 113--120.

```{r, results = "asis"}
bib[c("King1995")]
```

## `r weekList[3]`
```{r, results = "asis"}
bib["Geddes2010"]
```

## `r weekList[4]`
@Babbie2016, pp.89--113.

```{r, results = "asis"}
bib[c("Ragin2010")]
```
(Chapter 2)

## `r weekList[5]`
@Babbie2016, pp.124--135.

```{r, results = "asis"}
bib[c("Collier1997")]
```

## `r weekList[6]`
@Babbie2016, pp.135--152, 156--180.

```{r, results = "asis"}
bib[c("Adcock2001")]
```


## `r weekList[7]`
*Due for the research question approval: `r dates$Wed[7]`.*

```{r, results = "asis"}
bib[c("Seawright2014")]
```

Midterm Review

## `r weekList[8]`
Midterm.

@Babbie2016, pp.32--58.

## `r weekList[9]`

```{r, results = "asis"}
bib[c("Gerring2005", "Fearon1991")]
```

## `r weekList[10]`

@Babbie2016, pp.225--244.

```{r, results = "asis"}
bib[c("Gerber2011")]
```

## `r weekList[11]`

```{r, results = "asis"}
bib[c("Gerring2004")]
```

```{r, results = "asis"}
bib[c("Przeworski1970")]
```
31--39, 74--87.


## `r weekList[12]`

```{r, results = "asis"}
bib[c("Bennett2007", "Geddes2010")]
```

## `r weekList[13]`

*Due for the brief of the theory: `r dates$Mon[13]`.*

@Babbie2016, pp.307--320, 323--348 (Mon.), 382--408 (Wed.).


## `r weekList[14]`

## `r weekList[15]`

@Babbie2016, pp.411-430.

```{r, results = "asis"}
bib[c("Tang2016")]
```

## `r weekList[16]`

@Babbie2016, pp.487-507.

[Presentation at APSA 2014: Policy Bargaining and International Conflict](https://www.youtube.com/watch?v=bwNBXuz2eRg)

[Presentation at MPSA 2017: Trump Scenes](https://www.youtube.com/watch?v=Z4ISkF2H4tk)

## `r weekList[17]`
*Due for the research proposal: `r dates$Mon[17]`.*


\clearpage

# Rubric for In-Class Presentation {#id}

| Item                          | Criterion                                                                                                                                         | Grade |
|-------------------------------|--------------------------------------------------------------------------------------------------------------------------------------------------|-------|
| Duration                      | 5-10 mins 1; < 5 min 0.                                                                                                               | X     |
| Summary       | Clearly described the logic and main arguments 1; covered the main arguments 0.5; failed to capture the main arguments 0.                         | X     |
| Impressive point              | Clearly described impressive point(s) and explained why 1; mentioned the impressive point 0.5; not discuss the point at all 0.                   | X     |
| Critical thinking              | Clearly described the question and why it's important 1; posted a question 0.5; not raise any question 0.                                         | X     |                                                   |       |

# Rubric for Critical Response Paper {#id}

| Item                    | Criterion                                                                                                                      | Grade |
|-------------------------|-------------------------------------------------------------------------------------------------------------------------------|-------|
| Word Count | > 500 2; 300--500 1; <300 0        | X     |
| Summary | Clearly describe the logic and main arguments 2; cover the main arguments 1; fail to capture the main arguments 0        | X     |
| Learned point            | Clearly explain the learned points and their importance 2; clearly describe the points learned 1; no learned point mentioned 0 | X     |
| Relation with other materials | Clearly explained the relation with the topic of the week and other materials 2; mention another material 1; only talked about the assigned reading 0. | X     |
| Critical thinking       | Clear opinions and why 2; have a perspective of the reading 1; no perspective at all 0                                      | X     |


\clearpage

# Rubric for Research Proposal {#id}

| Item                            | Criterion                                                                                                                                                                                                            | Grade |
|---------------------------------|---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|-------|
| Cover Page (5%)                | Is the table fully filled? Is every element defined?                                                                                                                                                                | X     |
| Research Question Approval (5%) | Was the research proposal approved by 2017-10-09?                                                                                                                                                                   | X     |
| Brief of Theory (5%)            | Was the brief of the theory submitted by 2017-11-12?                                                                                                                                                                | X     |
| Introduction (10%)              | Is the research question well stated? Does the intro clearly explain the importance of the study? Does the intro clearly explain the potential contribution of this project?                                        | X     |
| Literature Review (10%)         | Does the LR address more than three existing studies? Does the LR clearly review the findings of the existing literature? Does the LR clearly state how the existing literature serve as the basis for this study?   | X     |
| Theory (15%)                    | Is the causal logic clearly stated? Are the concepts in the theory defined well? Is the causal chain complete and consistent? Are the causal inferences (hypotheses) clearly stated and consistent with the theory? | X     |
| Research Design (20%)           | Does the author clearly describe the strategy to test the hypotheses? Does the author defend his/her method choice well?                                                                                            | X     |
| Data (10%)                      | Is there a complete plan of data collection? How do the data fit the research design? Validations?                                                                                                                   | X     |
| Feasibility (5%)                | Is the research design a feasible one for a college student? What are the potential difficulties the researcher may encounter?                                                                                         | X     |
| Citation (10%)                   | Are the citations well presented? Is there a full bibliography attached? Are the citation and bibliography styles consistent with the APSR requirement?                                                             | X     |
| Overall writing (5%)           | Was the proposal proofread and edited? Are the paragraphs well framed and organized? Do the word count and layout match the requirement?                                                                                                  | X     |


\clearpage

# CLAS Teaching Policies & Resources — Syllabus Insert
## Administrative Home
The College of Liberal Arts and Sciences is the administrative home of this course and governs matters such as the add/drop deadlines, the second-grade-only option, and other related issues. Different colleges may have different policies. Questions may be addressed to 120 Schaeffer Hall, or see the CLAS Academic Policies Handbook at https://clas.uiowa.edu/students/handbook.

## Electronic Communication
University policy specifies that students are responsible for all official correspondences sent to their University of Iowa e-mail address (@ uiowa.edu). Faculty and students should use this account for correspondences ([Operations Manual, III.15.2](https://opsmanual.uiowa.edu/human-resources/professional-ethics-and-academic-responsibility#15.2), k.11).

## Accommodations for Disabilities
The University of Iowa is committed to providing an educational experience that is accessible to all students. A student may request academic accommodations for a disability (which includes but is not limited to mental health, attention, learning, vision, and physical or health-related conditions). A student seeking academic accommodations should first register with Student Disability Services and then meet with the course instructor privately in the instructor's office to make particular arrangements. Reasonable accommodations are established through an interactive process between the student, instructor, and SDS. See https://sds.studentlife.uiowa.edu/ for information. 

## Nondiscrimination in the Classroom
The University of Iowa is committed to making the classroom a respectful and inclusive space for all people irrespective of their gender, sexual, racial, religious or other identities. Toward this goal, students are invited to optionally share their preferred names and pronouns with their instructors and classmates. The University of Iowa prohibits discrimination and harassment against individuals on the basis of race, class, gender, sexual orientation, national origin, and other identity categories set forth in the University’s Human Rights policy. For more information, contact the Office of Equal Opportunity and Diversity, diversity@uiowa.edu, or visit [diversity.uiowa.edu](https://diversity.uiowa.edu/office/equal-opportunity-and-diversity).

## Academic Honesty
All CLAS students or students taking classes offered by CLAS have, in essence, agreed to the [College's Code of Academic Honesty](https://clas.uiowa.edu/students/handbook/academic-fraud-honor-code): "I pledge to do my own academic work and to excel to the best of my abilities, upholding the [IOWA Challenge](https://newstudents.uiowa.edu/iowa-challenge). I promise not to lie about my academic work, to cheat, or to steal the words or ideas of others; nor will I help fellow students to violate the Code of Academic Honesty." Any student committing academic misconduct is reported to the College and placed on disciplinary probation or may be suspended or expelled ([CLAS Academic Policies Handbook](https://clas.uiowa.edu/students/handbook)).

## CLAS Final Examination Policies
The final examination schedule for each class is announced by the Registrar generally by the fifth week of classes. Final exams are offered only during the official final examination period. No exams of any kind are allowed during the last week of classes. All students should plan on being at the UI through the final examination period. Once the Registrar has announced the date, time, and location of each final exam, the complete schedule will be published on the Registrar's web site and will be shared with instructors and students. It is the student's responsibility to know the date, time, and place of a final exam.

## Making a Suggestion or a Complaint
Students with a suggestion or complaint should first visit with the instructor (and the course supervisor), and then with the departmental DEO (Wenfang Tang, 335-2358). Complaints must be made within six months of the incident ([CLAS Academic Policies Handbook](https://clas.uiowa.edu/students/handbook)).

## Understanding Sexual Harassment
Sexual harassment subverts the mission of the University and threatens the well-being of students, faculty, and staff. All members of the UI community have a responsibility to uphold this mission and to contribute to a safe environment that enhances learning. Incidents of sexual harassment should be reported immediately. See the UI [Office of the Sexual Misconduct Response Coordinator](https://osmrc.uiowa.edu/) for assistance, definitions, and the full University policy.

## Reacting Safely to Severe Weather
In severe weather, class members should seek appropriate shelter immediately, leaving the classroom if necessary. The class will continue if possible when the event is over. For more information on Hawk Alert and the siren warning system, visit the [Department of Public Safety website](https://police.uiowa.edu/emergency-communications).


\clearpage

# Reference
