---
output: 
  bookdown::pdf_document2:
    keep_tex: true
    fig_caption: yes
    latex_engine: pdflatex
    template: D:/MEGAsync/Dropbox/07_usefulNotes/svm-latex-syllabus.tex
geometry: margin=1in

title: "POLI 2000: Designing Political Research"
author: Yue Hu
date: "Fall 2017"
email: "yue-hu-1@uiowa.edu"
#web: "svmiller.com/teaching"
officehours: "12:30 -- 15:30 M"
office: "313 Shaeffer Hall"
classroom: "105 EPB"
classhours: "15:30 -- 16:45 MW"
fontsize: 11pt
biblio-style: ajps
bibliography: readings.bib
header-includes:
   - \linespread{1.05}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(pacman)
p_load(dotwhisker, ggplot2, interplot,# Visualization
       lubridate, RefManageR,# Applied
       # dependency
       readxl, haven, descr, stringi, stringr, arm, car, stargazer,
       broom, tidyverse) # data wrangling

set.seed(313)

# Bib setting
ajps_mimic <- RefManageR:::MakeBibLaTeX()
with(ajps_mimic,{
  ajps_mimic$fmtJournal <- function(s){
                                if (length(s$journaltitle)) {
                                    res <- emph(cleanupLatex(s$journaltitle))
                                    if (length(s$journalsubtitle))
                                        res <- paste(addPeriod(res), emph(cleanupLatex(s$journalsubtitle)))
                                    return(res)
                                }
                                else if (!is.null(s$journal)) {
                                    emph(cleanupLatex(s$journal))
                                }
     }
     
     ajps_mimic$fmtURL <- function (paper) {
        if (length(paper[["url"]])) {
            res <- paper$url
            res <- switch(docstyle, html = paste0("\\url{", 
                res, "}"), markdown = paste0("[", res, "](", 
                res, ")"), paste0("\\url{", res, "}"))
            if (length(paper$urldate)) {
                fDate <- try(ProcessDate(paper$urldate, NULL), TRUE)
                if (!is.null(fDate) && !inherits(fDate, "try-error")) 
                    res <- paste0(res, " (visited on ", DateFormatter(fDate, 
                      TRUE), ")")
            }
            addPeriod(res)
        }
        else if (length(paper$urldate)) {
            fDate <- try(ProcessDate(paper$urldate, NULL), TRUE)
            if (!is.null(fDate) && !inherits(fDate, "try-error")) 
                paste0("(Visited on ", DateFormatter(fDate, TRUE), 
                    ").")
        }
     }
     
     ajps_mimic$fmtLanguage <- function(lang) {
    if (length(lang) && tolower(lang) != "english") 
        paste0("[", sub("\\b(\\w)", "\\U\\1", lang, perl = TRUE, 
            useBytes = TRUE),"]")
       }
     
     ajps_mimic$formatArticle <- function (paper) {
    collapse(c(fmtPrefix(paper), fmtBAuthor(paper), fmtJTitle(paper$title), fmtLanguage(paper$language), 
        fmtAddOn(paper$titleaddon),
        fmtTranslator(paper), fmtCommentator(paper$commentator), 
        fmtAnnotator(paper$annotator), fmtVersion(paper$version), 
        sentenceP(paste0(c(paste0(c(fmtJournal(paper), fmtSeries(paper$series)), 
            collapse = ""), fmtVolume(paper$volume, paper$number), 
            fmtJournDate(paper)), collapse = " "), fmtBTitle(paper$issuetitle, 
            paper$issuesubtitle), fmtEditor(paper, suffix = NULL, 
            prefix = ". "), fmtNote(paper$note, prefix = ". ", 
            suffix = NULL), pgs = fmtPages(paper$pages, paper$pagination), 
            sep = ""),fmtURL(paper), fmtAddendum(paper$addendum), 
        fmtPubstate(paper$pubstate)))
     }
     
     ajps_mimic$formatArticle <- function (paper) {
    collapse(c(fmtPrefix(paper), fmtBAuthor(paper), fmtJTitle(paper$title), fmtLanguage(paper$language), 
        fmtAddOn(paper$titleaddon),
        fmtTranslator(paper), fmtCommentator(paper$commentator), 
        fmtAnnotator(paper$annotator), fmtVersion(paper$version), 
        sentenceP(paste0(c(paste0(c(fmtJournal(paper), fmtSeries(paper$series)), 
            collapse = ""), fmtVolume(paper$volume, paper$number), 
            fmtJournDate(paper)), collapse = " "), fmtBTitle(paper$issuetitle, 
            paper$issuesubtitle), fmtEditor(paper, suffix = NULL, 
            prefix = ". "), fmtNote(paper$note, prefix = ". ", 
            suffix = NULL), pgs = fmtPages(paper$pages, paper$pagination), 
            sep = ""),fmtURL(paper), fmtAddendum(paper$addendum), 
        fmtPubstate(paper$pubstate)))
     }
     
     ajps_mimic$formatUnpublished <- function (paper) {
        collapse(c(fmtPrefix(paper), fmtBAuthor(paper), fmtIBTitle(paper$title, 
            paper$subtitle, FALSE), fmtAddOn(paper$titleaddon), fmtLanguage(paper$language), 
            fmtHowPublished(paper$howpublished), fmtNote(paper$note), 
            sentence(fmtPublisher(NULL, paper$location, paper$address), sep = ""), fmtDOI(paper$doi), 
            fmtURL(paper), fmtAddendum(paper$addendum), fmtPubstate(paper$pubstate)))
     }
     
     ajps_mimic$formatMisc <- function (paper) {
    collapse(c(fmtPrefix(paper), fmtBAuthor(paper), fmtIBTitle(paper$title, 
            paper$subtitle, FALSE), fmtAddOn(paper$titleaddon), fmtLanguage(paper$language), 
        fmtEditor(paper, !length(paper$author)), fmtHowPublished(paper$howpublished), 
        addPeriod(fmtType(paper$type)), fmtVersion(paper$version), 
        fmtNote(paper$note), sentence(fmtPublisher(paper$organization, 
            paper$location, paper$address), fmtDate(attr(paper, 
            "dateobj")), sep = ""), fmtDOI(paper$doi), fmtEprint(paper), 
        fmtURL(paper), fmtAddendum(paper$addendum), fmtPubstate(paper$pubstate)))
}
})


tools::bibstyle("ajps_mimic", ajps_mimic)

bib <- ReadBib("readings.bib", check = FALSE)
BibOptions(check.entries = FALSE, 
           first.inits = FALSE,
           bib.style = "ajps_mimic",
           style = "latex",
           max.names = 4,
           dashed = FALSE,
           sorting = "ydnt")
```

```{r calendar, include=FALSE}
# Opening Date: 2017-08-21 ####
start <- ymd("2017-08-21")
# Final Week: 2017-12-11 ####
end <- ymd("2017-12-17")

dates <- data.frame(day = seq(from = start, to = end, by = "days")) %>%
  mutate(day = ymd(day), weekDay = wday(day), weekNum = week(day)) %>% # get the relative week number
  mutate(weekNum = weekNum - (min(weekNum) - 1)) %>%
    filter(weekDay %in% c(2,1)) %>% # only keep Monday and Friday
      spread(key = weekDay, value = day) %>% # long to wide
        rename(Sun = `1`, Mon = `2`) %>%
          mutate(Sun = lead(Sun)) # get the Sundays to the correct rows
      
dates <- dates[c("weekNum", "Mon", "Sun")] %>% # reorder colums
  na.omit

dates$content <- NA
## Holidays
dates$content[dates$Mon == ymd("2017-09-04")] <- "What's A Good Question (Labor Day)"
dates$content[dates$Mon == ymd("2017-11-20")] <- "Thanks Giving Week"
dates$content[dates$Mon == ymd("2017-12-11")] <- "Final Week"

dates$content[is.na(dates$content)] <- c("Being a Political Scientist", "Being Scientific", "How to Find Research Question", "Concepts", "Measurement", "Theory", "Experimental Logic and Design", "Principles of Case Study", "Case Study in Practice", "Content Analysis", "Large-N Analysis", "Profession", "Presentation", "Presentation")

weekList <- paste0("Week ", dates$weekNum, " (", dates$Mon, "~", dates$Sun, "): ", dates$content)
```
# Overview
Why do candidates win elections? Why do states get involved in international crises and wars? Why do states cooperate on transnational problems like climate change? What explains differences in how countries treat their citizens? What explains the choices of violent non-state actors like terrorists? There are just some of the questions that political scientists study. The goal of this course is for you to understand how political scientists study these questions. This course will introduce students to political science research and the many different ways that research is undertaken.

This class will help students understand how social scientists study political phenomena. You will learn how to develop causal explanations about politics and society, develop testable research hypotheses, and design different approaches to empirically studying these theories. Emphasis will be on an active hands-on learning environment (TILE classroom). You will also be able to more fully understand research that is produced in Political Science.

# Requirements
I will base your grade for the course on your performance in the four areas below. For each component of the course grade, I assign a numerical score. I then calculate the course grade with the weighted average of the component scores. Scores of 90-100 correspond to A, 80-89 to B, etc., with plusses and minuses for the top and bottom third of each decile.

1. Class attendance and performance (30%: 10% participation + 10% leading discussion + 10% attendance). 
Regarding participation, I am looking for you to show that you have read and critically evaluated the assigned readings and are engaged with our in-class discussions.
Each student will 

1. In-class quizes (24%)

1. Midterm examination (20%)

1. Final examination (26%)

# Readings
## Required textbook:
```{r, results = "asis"}
bib[c("Babbie2012", "VanEvera1997")]
```

## `r weekList[1]`
```{r, results = "asis"}
bib[c("Dryzek2006", "Keohane2009")]
```

*Recommanded:*

```{r, results = "asis"}
bib[c("Weber1968", "Weber1946")]
```

## `r weekList[2]`
@Babbie2012, pp.1-27, 112-120.

*Recommanded:*

```{r, results = "asis"}
bib[c("Lakatos1970")]
```

## `r weekList[3]`
```{r, results = "asis"}
bib["Geddes2010"]
```

@VanEvera1997, pp.97-99.

## `r weekList[4]`
@Babbie2012, pp.91-112.

```{r, results = "asis"}
bib[c("Ragin2010")]
```
(Chapter 1, 2)

## `r weekList[5]`
@Babbie2012, pp.165-177.

```{r, results = "asis"}
bib[c("Sartori1970", "Collier1993", "Collier1997")]
```

*Recommanded:*

```{r, results = "asis"}
bib[c("Bachrach1962", "Barnett2005")]
```

## `r weekList[6]`
@Babbie2012, pp.177-194, 197-223.


## `r weekList[7]`
@VanEvera1997, pp.7-50.

Midterm Review

## `r weekList[8]`
Midterm.

@Babbie2012, pp.271-291.

*Recommonded:*

```{r, results = "asis"}
bib[c("Mintz2004", "Mintz2006")]
```

## `r weekList[9]`
@VanEvera1997, pp.49-88.


## `r weekList[10]`

## `r weekList[11]`

## `r weekList[12]`

## `r weekList[13]`

## `r weekList[14]`

## `r weekList[15]`

## `r weekList[16]`

## `r weekList[17]`

